Z-Resonance at LEP

### 2010-07-20 Z0-Publikation/tex/paper-template.tex

@@

The standard model of elementary particles describes interactions of particles
by four fundamental forces. One of them is the electroweak force. It`s gauge
bosons, which mediate the force between the two interacting particles, are the
photon as well as the W$^{\pm}$- and the Z$^0$-boson. At the
electron-positron-collider the Z$^0$ has been seen for the first time, which was
possible because of the sufficient center of mass energy of this collider
experiment.

@@

Z can decay via ....
and can be observed at ...
The LEP is ....
The L3 detector consists of ...
.....
\section{ Data analysis}

The decay of the Z in the channel ... was studied...
The cuts used are described ...

>>>>

\newcommand{\dd}[1]{\mathrm{d}#1\,} % declare dx operator, usage: \dd{x} for dx
\newcommand{\lref}[1]{listing (\ref{lst:#1})} % refer to a listing, usage:\lref{label} for Listing (...)
\newcommand{\fref}[1]{fig. (\ref{fig:#1})} % refer to a figure, usage:\lref{label} for Abb. (...)
\newcommand{\tref}[1]{tab. (\ref{tab:#1})} % refer to a table, usage:tlref{label} for Tab. (...)
\newcommand{\eref}[1]{eq. (\ref{eqn:#1})} % refer to a equation, usage:\eref{label} for Gl. (...)

@@

The standard model of elementary particles describes interactions of particles
by four fundamental forces. One of them is the electroweak force. It`s gauge
bosons, which mediate the force between the two interacting particles, are the
photon as well as the W$^{\pm}$- and the Z$^0$-boson. At the
electron-positron-collider LEP at CERN the Z$^0$ has been seen for the first
time, which was possible because of the sufficient center of mass energy of this
collider experiment.

@@

The Z$^0$-particle, which was supposed to be produced at LEP, can decay in
various ways. One of these possibilities is the decay via two different quarks 
(Z$^0→q\overline{q'}$), another one could be the decay via two charged leptons
like Z$^0→ μ^+μ^-$. The first one of the mentioned decays can be seen
as two jets which can be measured in hadronic calorimeters. The leptonic decay
is measured due to registration of leptons in electromagnetic calorimeters.

The detector for all of these particles is the LEP. It`s structure can be seen
in \fref{aufbau}.
\begin{figure}[htb]
 \centering
 \includegraphics[page=5,viewport=286 620 508 765,clip,%
  width=\columnwidth,keepaspectratio]{../../Z0/docs/Z0ResFprakt}
 \caption{Design of the L3 detector\cite{script}}
 \label{fig:aufbau}
\end{figure}
There are layers of components with different purposes, starting from the
vertex point, these are the tracking chamber, the electromagnetic calorimeter,
the hadronic calorimeter and finally the muon chamber.

The LEP is ....
The L3 detector consists of ...
.....
\section{ Data analysis}

For a detailed analysis of the mentioned processes it is important to be able
to distinguish between muonic and hadronic decays, we did some Monte Carlo
studies to figure out how these processes look like. This gave us the
possibility to apply cuts on the measured distributions.
